Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-05-07 review/response/response.tex

\documentclass{scrartcl}

\begin{document}

\title{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}
\subtitle{Rebuttal to Reviewers}

\author{JC Lock; G. Cielniak; ID Gilchrist; N Bellotto}

\maketitle

@@

\noindent Dear associate editors and reviewers,

We would first like to sincerely thank you for your honest and helpful feedback on our work.
We have taken some time to go over and implement your suggestions and we believe that we can resubmit to you an improved version of the paper. 
Please find below our responses to your comments and suggestions, where we point out how we addressed them.

@@

  \item \textit{To my mind, the paper is a bit of an “LPU” (least-publishable-unit), for a larger, more interesting project (which I would love to see!). The specific contribution here is in the use of a pitch gradient for conveying elevation information for spatialized 3D audio as well as a user study evaluating its effectiveness and some of the design space (three different pitch gradients). I’m not sure that I would consider this an adequate contribution for a shorter conference paper (such as ASSETS); for TACCESS, this seems weak. That is, I would say the contribution is not commensurate with the length of the paper.}
  \item[] On this front, we again have to respectfully disagree with the reviewer's opinion.
    We pointed out in the previous work section that researchers have implemented different combinations of spatialised sound, frequency adjustments and headphones in their navigation systems for people with visual impairment with different levels of success.
    However, to our knowledge, very little work has been done in quantifying these spatialised audio signals with varying pitch gains with a significant number of participants with or without visual impairments, as well as bone-conduction headphones.
    Indeed, we believe that the experiment design, analysis and scale is a fairly novel contribution to other researchers that wish to know what level of perception they can expect from audio signals played back via bone-conduction headphones.
    It is not our intention to minimise the work to an 'LPU' and indeed, this paper represents a phase of work that was completed for a larger overall project.
    However, in our opinion it would be detrimental to the message we'd like to publish to the scientific community if we include too much detail on the overall project and bog the reader down in details that are not pertinent to this publication.

\end{itemize}

\section*{Reviewer 3}

\begin{itemize}
  \item \textit{The contents in Fig. 6 and Fig. 7 are confusing. They both show the median cut-off. Since they have different units (one is semitone and the other is Hz), is the median cut-off the same? Explain this threshold more clearly.}

  \item[] We used a linear scale in Figure 7 to highlight the separation between the 3 settings, which was not as clearly evident with the logarithmic semitone scale.
    This has been clarified in section 5.2.

  \item \textit{The contents in Fig 5 and Fig. 6 are confusing. Fig. 5 shows that the number of wrong guesses is much bigger than that of correct guesses. Does it mean that the pitch is hard to be distinguished? It also shows that the number of wrong guesses mostly locates in the area where the pitch difference is almost 0. Intuitively, with the increase of pitch difference, the correct guesses should be increased as well. But in Fig. 6, it shows that most of the samples (75\% the correct guesses) are in the area with smaller pitch threshold e.g 0 to 0.5, rather than in the areas with larger pitch threshold e.g. 1.0-2.0.}
  \item[] Given the progressive difficulty process we used, the tones became increasingly more difficult to distinguish from one another, i.e. small frequency difference represented by a small semitone and Hz difference.
    In Fig 6, it shows the threshold where 75\% of the correct guesses lie to the right, i.e. the larger semitone differences that are easier to distinguish.

  \item \textit{Before equation (3), the authors claim the targets have no width. So does it mean that the virtual objects are actually a virtual point randomly created in the Tango’s screen? Since the Tango has an RGB-D camera to measure both direction and distance, a more practical experiment design should use the real daily objects.}
  \item[] This is correct, we use virtual targets generated by the Tango.
    We opted for this setup over physical targets, since piratically it was advantageous and allowed us to easily place many targets at a variety of random locations while still knowing precisely where the targets are generated, since they are all located relative to the Tango's frame of reference. 
    For these pointing experiments, it was sufficient, but in a larger-scale experiment with a real object search system, real objects would indeed make more sense than virtual ones.

  \item \textit{Improve the resolution of Fig. 8 to make it more clear.}
  \item[] Fig 8 has been updated with this change. 
\end{itemize}

\bibliography{bib}
\bibliographystyle{ieeetr}

### 2020-05-07 paper.tex
Edits to reviews

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{todonotes}

@@

The main contributions of this paper are two-fold: 
\begin{itemize}
  \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's elevation angle when using a mobile device with a bone-conducting headset; 
  \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
\end{itemize}

@@

\noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre}, but the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
Previous authors have found this to capture the true performance metrics fairly well~\citep{zhai2004speed}.}
Fitts's index of performance, $IP$, can then be calculated using

@@

Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones. 
It can also be used to improve the interface's frequency profile and performance. 
\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
\cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
\hlbreakable{Note that the cut-off thresholds in \cref{fig:pitch-thresholds-hist} are transformed from the logarithmic semitone scale in \cref{fig:pitch-thresholds} to a linear Hertz-based scale for visualisation purposes to make the separation between the settings more clearly visible.}

@@

\begin{table}
  \centering
  \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
	\begin{tabular}%
	{>{\centering\arraybackslash}p{0.5cm}%
	 >{\centering\arraybackslash}p{1.5cm}%
	 >{\centering\arraybackslash}p{1.1cm}%
 	 >{\raggedleft\arraybackslash}p{2.6cm}%
 	 >{\raggedleft\arraybackslash}p{3.0cm}%
	 >{\raggedleft\arraybackslash}p{3.0cm}}
    \toprule
    &           & Setting      & Mean Angle Error [rad] & Mean Absolute Angle Error [rad] &  Pearson Correlation \\ \midrule
    \multirow{6}{*}{\textit{G1}}
    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.25\pm0.27$ & $0.75,~p < 0.001$ \\
    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.26\pm0.27$ & $0.77,~p < 0.001$ \\
    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.26\pm0.29$ & $0.72,~p < 0.001$ \\ \cline{2-6}
    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.42\pm0.31$ & $0.36,~p < 0.001$ \\
    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.44\pm0.24$ & $0.49,~p < 0.001$ \\
    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.36\pm0.29$ & $0.48,~p < 0.001$ \\ \midrule
    \multirow{6}{*}{\textit{G2}}
    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.48\pm0.31$ & $0.10,~p = 0.03$  \\
    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.45\pm0.27$ & $0.13,~p = 0.01$  \\
    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.36\pm0.22$ & $0.21,~p < 0.001$ \\\cline{2-6}
    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.49\pm0.39$ & $0.03,~p = 0.48$  \\
    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.42\pm0.33$ & $0.31,~p < 0.001$ \\
    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.36\pm0.32$ & $0.40,~p < 0.001$ \\ 
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage[capitalise]{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{todonotes}

@@

The main contributions of this paper are two-fold: 
\begin{itemize}
  \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's elevation angle when using a mobile device with a bone-conducting headset; 
  \item we show that this sound-based human-machine interface exhibits a response that is well-modelled by Fitts's Law which can provide a useful metric of performance for similar mobile user interfaces.
\end{itemize}

@@

\noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, the on-target tone was emitted.
This is similar to the work by~\citet{kabbash1995prince}, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
However, the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
Previous authors have found this to capture the true performance metrics fairly well~\citep{zhai2004speed}.}
Fitts's index of performance, $IP$, can then be calculated using

@@

Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones. 
It can also be used to improve the interface's frequency profile and performance. 
\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group.

\begin{highlighted}
For the target search experiment, the pitch differences between the \SI{512}{\hertz} on-target tone and the participants' selected tones were collected and their cut-off threshold were determined in a similar way.
Each participant's median tone error for each setting was then plotted alongside the groups' median thresholds and plotted in \cref{fig:pitch-thresholds-hist}.
These data are plotted on a linear Hertz-based scale instead of a semitone scale to highlight the grouping between the three settings.
\end{highlighted}

@@

\begin{table}
  \centering
  \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
	\begin{tabular}%
	{>{\centering\arraybackslash}p{0.5cm}%
	 >{\centering\arraybackslash}p{1.2cm}%
	 >{\centering\arraybackslash}p{0.9cm}%
 	 >{\raggedleft\arraybackslash}p{2.2cm}%
 	 >{\raggedright\arraybackslash}p{2.6cm}%
	 >{\raggedright\arraybackslash}p{2.6cm}}
    \toprule
    &           & Setting      & Mean Angle Error [rad] & Mean Absolute Angle Error [rad] &  Pearson Correlation \\ \midrule
    \multirow{6}{*}{\textit{G1}}
    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.25\pm0.27$ & $0.75,~p < 0.001$ \\
    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.26\pm0.27$ & $0.77,~p < 0.001$ \\
    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.26\pm0.29$ & $0.72,~p < 0.001$ \\ \cline{2-6}
    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.42\pm0.31$ & $0.36,~p < 0.001$ \\
    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.44\pm0.24$ & $0.49,~p < 0.001$ \\
    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.36\pm0.29$ & $0.48,~p < 0.001$ \\ \midrule
    \multirow{6}{*}{\textit{G2}}
    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.48\pm0.31$ & $0.10,~p = 0.03$  \\
    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.45\pm0.27$ & $0.13,~p = 0.01$  \\
    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.36\pm0.22$ & $0.21,~p < 0.001$ \\\cline{2-6}
    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.49\pm0.39$ & $0.03,~p = 0.48$  \\
    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.42\pm0.33$ & $0.31,~p < 0.001$ \\
    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.36\pm0.32$ & $0.40,~p < 0.001$ \\ 
    \bottomrule
  \end{tabular}
\end{table}
